### 2010-11-18 doc/tech_doc/a-rex/arex_tech_doc.tex
update instructions with how to run WS-interface through arc.conf

The A-REX service is a pluggable module of the HED, so it is first
required to set up HED configuration, and add the A-REX elements. To
add A-REX to an existing HED configuration, add a new \verb|<Name>|
element inside \verb|<Plugins>| containing the string
\emph{arex}. This will make HED load the libarex plugin library.

@@

The A-REX can process jobs submitted through a traditional GridFTP
server instead of, or as well as, the WS interface. The GridFTP/Grid
Manager server packages can be installed alongside A-REX packages, so
it is easy to switch between the two. The configuration of the GridFTP
server is in the same legacy \emph{arc.conf} configuration file as is
used by the A-REX, and configuration instructions are given
in~\cite{gm}. In general no configuration changes are necessary to use
a Grid Manager-configured GridFTP server with the A-REX.

If it is desired to run both WS and GridFTP interfaces at the same
time, simply setup and start the A-REX as described in the previous
section, then start the GridFTP server. If only the GridFTP interface
is to be used, then the special \emph{a-rex} command should be used
(rather than \emph{arched}).

This command automatically creates a HED configuration for running the
A-REX without the WS interface, and so no manual HED configuration
needs to be done. The GridFTP server should then be started.

>>>>

The A-REX service is a pluggable module of the HED, so it is first
required to set up HED configuration, and add the A-REX elements. HED
configuration is in an XML format, however a special comand \emph{a-rex} has
been written which automatically creates a HED configuration for running the
A-REX from an existing arc.conf file used by the Grid Manager, and so no manual
XML configuration editing needs to be done. To enable the WS interface the
following line must be added to the arc.conf configuration file:

\begin{itemize}
  \item \textbf{\textit{arex\_mount\_point}}\textit{=path}
\end{itemize}

where \emph{path} is the A-REX service endpoint, for example
\verb|https://your.host:60000/arex|. Then the A-REX can be started

It is also possible to write configuration directly in XML. To add A-REX to an
existing HED configuration, add a new \verb|<Name>| element inside
\verb|<Plugins>| containing the string \emph{arex}. This will make HED load the
libarex plugin library.

@@

The A-REX can process jobs submitted through a traditional GridFTP interface
instead of, or as well as, the WS interface. The A-REX version of the ARC GridFTP
server (\verb|a-rex-gridftpd|) must be used instead of the Grid Manager server.
However, the GridFTP/Grid Manager server packages can be installed alongside
A-REX packages, so it is easy to switch between the two. The configuration of the
GridFTP server is in the same legacy \emph{arc.conf} configuration file as is
used by the A-REX, and configuration instructions are given in~\cite{gridftpd}.
In general no configuration changes are necessary to use a Grid
Manager-configured GridFTP server with the A-REX.

If it is desired to run both WS and GridFTP interfaces at the same time, simply
setup and start the A-REX as described in the previous section, then start the
GridFTP server. If only the GridFTP interface is to be used, then the special
\emph{a-rex} command should be used (rather than \emph{arched}) to start A-REX.
The GridFTP server should then be started.
